Proposal: An Analysis of Hockey's Most Controversial Statistic

### 2024-09-26 proposal/project_proposal.tex
small changes to data and added to research

\paragraph{Specific Aims}
Formulate your research question;
translate your research question into statistical/data science questions

The goal of this project is to evaluate the effectiveness of the plus/minus statistic. Some of the information
I am trying to determine is if the plus/minus statistic can be used to determine how good a player is both on
offense and defense. I also want to see if the plus/minus has any validity being used as an individual
statistic or as a team statistic. Based on my observations, I will compare the plus/minus statistic to other
statistics that have a similar purpose such as CORSI or Fenwick.
These questions are critical as plus/minus is used in scouting and analysis, but its reliability 
has been debated. By comparing it with modern metrics, I aim to shed light on its true value in player evaluation.

@@

I am using data from the National Hockey League (NHL). The data is collected from a website called Natural Stat Trick. 
I collected data from the 2021-2022, 2022-2023, and 2023-2024 seasons. I am particularly interested in the advanced hockey 
statistics that are collected for each player in the NHL. These statistics include CORSI, Fenwick, high-danger chances,
shooting percentages, and more.

\paragraph{Research Design and Methods}
What design or methods will you use?

>>>>

\paragraph{Specific Aims}
The goal of this project is to evaluate the effectiveness of the plus/minus statistic. Some of the information
I am trying to determine is if the plus/minus statistic can be used to determine how good a player is both on
offense and defense. I also want to see if the plus/minus has any validity being used as an individual
statistic or as a team statistic. Based on my observations, I will compare the plus/minus statistic to other
statistics that have a similar purpose such as CORSI or Fenwick.
These questions are critical as plus/minus is used in scouting and analysis, but its reliability 
has been debated. By comparing it with modern metrics, I aim to shed light on its true value in player evaluation.

@@

I am using data from the National Hockey League (NHL). The data is collected from the websites Natural Stat Trick and NHLEdge. 
I collected data from the 2021-2022, 2022-2023, and 2023-2024 seasons. I am particularly interested in the advanced hockey 
statistics that are collected for each player in the NHL. These statistics include CORSI, Fenwick, high-danger chances,
shooting percentages, and more. This data will also include more basic statistics such as points, goals, assists, plus/minus,
time on ice, etc.

\paragraph{Research Design and Methods}
The first step of the project is to collect all relevant data. In this case, I will be exporting the data from all players
from the 2021- 2024 seasons into an Excel or csv file. Once the data has been collected, it needs to be cleaned. After the
data has been prepared, I can start some initial analysis to see what variables are correlated and where issues of collineairty 
exist, since this will effect which models and variables I use.
